API design for machine learning software: experiences from the scikit-learn project

### 2013-06-24 paper.tex
Remove manual page breaks.
affiliations (mine and @pprett's)

\institute{University of Amsterdam \and
           University of Liège \and
           Kobe University \and
           Parietal, INRIA Saclay \and
           University of Bonn \and
           Nuxeo \and 
           University of Bucharest \and
           Bauhaus-Universitat \and
           Telecom ParisTech \and
           University of Ballarat \and
           University of Washington \and
           Samsung Electronics Research Institute}

@@

To illustrate the initialize-fit sequence,
let us consider a supervised learning task using logistic regression.
Given the API defined above, solving this problem is as simple as the following
example.
\newpage
\begin{pythoncode}
from sklearn.linear_model import LogisticRegression

@@

Some unsupervised learning estimators may also implement the \texttt{predict}
interface. The code in the snippet below fits a $k$-means model with $k=10$ on
training data \texttt{X\_train}, and then uses the  \texttt{predict} method to
obtain cluster labels (integer indices) for unseen data \texttt{X\_test}.
\newpage
\begin{pythoncode}
from sklearn.cluster import KMeans

@@

\texttt{Pipeline} and \texttt{FeatureUnion} can be
combined to create complex and nested workflows.
The following snippet illustrates how to create a complex estimator
that computes both linear PCA and kernel PCA features on \texttt{X\_train}
(through a \texttt{FeatureUnion}),
selects the 10 best features in the combination according to an ANOVA test
and feeds those to an $\ell_2$-regularized logistic regression model.
\newpage
\begin{pythoncode}
from sklearn.pipeline import FeatureUnion, Pipeline
from sklearn.decomposition import PCA, KernelPCA
from sklearn.feature_selection import SelectKBest

>>>>

\institute{Informatics Institute, University of Amsterdam \and
           University of Liège \and
           Kobe University \and
           Parietal, INRIA Saclay \and
           University of Bonn \and
           Nuxeo \and 
           University of Bucharest \and
           Ciuvo GmbH \and
           Telecom ParisTech \and
           University of Ballarat \and
           University of Washington \and
           Samsung Electronics Research Institute}

@@

To illustrate the initialize-fit sequence,
let us consider a supervised learning task using logistic regression.
Given the API defined above, solving this problem is as simple as the following
example.
\begin{pythoncode}
from sklearn.linear_model import LogisticRegression

@@

Some unsupervised learning estimators may also implement the \texttt{predict}
interface. The code in the snippet below fits a $k$-means model with $k=10$ on
training data \texttt{X\_train}, and then uses the  \texttt{predict} method to
obtain cluster labels (integer indices) for unseen data \texttt{X\_test}.
\begin{pythoncode}
from sklearn.cluster import KMeans

@@

\texttt{Pipeline} and \texttt{FeatureUnion} can be
combined to create complex and nested workflows.
The following snippet illustrates how to create a complex estimator
that computes both linear PCA and kernel PCA features on \texttt{X\_train}
(through a \texttt{FeatureUnion}),
selects the 10 best features in the combination according to an ANOVA test
and feeds those to an $\ell_2$-regularized logistic regression model.
\begin{pythoncode}
from sklearn.pipeline import FeatureUnion, Pipeline
from sklearn.decomposition import PCA, KernelPCA
from sklearn.feature_selection import SelectKBest
